---
title: "Machine Learning with caret and recipes"
subtite: "Practical Data Science Meetup"
author: "Michael Levy  |  @ucdlevy"
date: "2017-11-02"
output:
  rmdshower::shower_presentation:
  self_contained: false
# katex: true
ratio: 16x10
---

```{r setup, include = FALSE}
library(tidyverse)
library(knitr)
library(caret)
library(recipes)
opts_chunk$set(echo = FALSE, warning = FALSE, cache = TRUE, 
               fig.asp = 1, fig.width = 4)
# Data source: https://archive.ics.uci.edu/ml/machine-learning-databases/pima-indians-diabetes/pima-indians-diabetes.data
d <- read_csv("https://archive.ics.uci.edu/ml/machine-learning-databases/pima-indians-diabetes/pima-indians-diabetes.data",
              col_names = c("num_pregnancies", "glucose_challenge", "BP", "skin_fold",
                            "insulin", "BMI", "diabetes_pedigree", "age", "diabetes"))
write_csv(d, "pima.csv")
# Replace impossible zeros with NA:
for (column in c("BP", "skin_fold", "insulin", "BMI", "age"))
  d[[column]][d[[column]] == 0] <- NA
```




## Machine Learning with `caret` & `recipes`

<img src="https://media.istockphoto.com/photos/carrot-isolated-picture-id166106089?k=6&m=166106089&s=612x612&w=0&h=QyF1Ktkjyez28_Wo5O6skqFta5XDEnyxPoUpfYRgj8A=" class="cover">

<p class="black">
Michael Levy  |  @ucdlevy  
SLC Practical Data Science Meetup  
2017-11-02
</p>

## What is `caret`?

> The caret package (short for _C_lassification _A_nd _RE_gression _T_raining) is a set of functions that attempt to streamline the process for creating predictive models.

Extensive documentation: topepo.github.io/caret

## What is `recipes`?

> The recipes package is an alternative method for creating and preprocessing design matrices that can be used for modeling or visualization.

- Grew out of `caret`'s preprocessing functionality. 
  - Comprehensive
  - Sequential
  - Efficient
  - `tidyverse`-style API

## A dataset

```{r summary, include = FALSE}
summary(d)
```

